\documentclass[11pt]{article}

\usepackage{amssymb}   % Extra symbols

%%% Define nice check and check box
\newcommand{\MyCheckedBox}{\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{0.1em}$\checkmark$}}
\newcommand{\MyCheckBox}{\makebox[0pt][l]{$\square$}\raisebox{.15ex}}

%%% Define check list
\setlength{\marginparwidth}{1.2in}
\let\oldmarginpar\marginpar
\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft #1]%
{\raggedright #1}}    

\newenvironment{checklist}{%
  \begin{list}{}{}% whatever you want the list to be
  \let\olditem\item
  \renewcommand\item{\olditem -- \marginpar{\MyCheckBox} }
  \newcommand\checkeditem{\olditem -- \marginpar{\MyCheckedBox} }
}{%
  \end{list}
}

\begin{document}

\section{Experiments}

\subsection{Occurrence extraction}
\begin{checklist}
    \item Manually annotate occurrences in a Fine Roll.
    \item Extract occurrences using parser.
    \item Describe results in terms of precision and recall.
    \item Discuss the results relating it to the simplicity of the parser and tell whether something more sophisticated is required.
\end{checklist}

\subsection{Name learning}
\begin{checklist}
    \item Learn surnames and first names by alternating parsing.
    \item Use the first names list from Fine Rolls on Gascon Rolls.
    \item Manually inspect the results obtained.
\end{checklist}

\subsection{Blocking}
\begin{checklist}
    \item Comparison of the three described blocking methods.
    \item Goals of these experiments is to find a suitable one for historical record linkage.
\end{checklist}

\subsection{Classification}
\begin{checklist}
    \item Record Linkage in Fine Rolls.
\end{checklist}

\subsection{Maximally informative k-itemsets}
\begin{checklist}
    \item Extract mikis from Wikipedia and Fine rolls datasets.
    \item Discuss the outcomes (anecdotal evidence).
    \item Discuss the "common name" problem and show how prevalent it is in the Wikipedia dataset.
    \item Take the "John Smith" group in Wikipedia and perform record linkage with mikis.
\end{checklist}

\subsection{Transitive closure}
\begin{checklist}
    \item How big is the problem of inconsistencies in the results obtained thusfar?
    \item Exploit transitive closure?
\end{checklist}

\end{document}