\documentclass{article}

\begin{document}

\begin{itemize}
    \item \cite{Winchester1970} page 4 explains the use of documenting the steps that lead to the linkage of records and gives an example of a project.
    \item \cite{Winchester1970} studies record linkage from the perspective of a historian. It is noted that though the record linkage task seems trivial, in practice it is often hard to execute manually. In the same paper this exemplified with a few truly linked records pairs: Yelverton, J.H.P.G. (turner)/Silvester, J.H.P.G. (sawyer); Horan, Michael (laborer)/Hograth, Michael (laborer); Mayplant, William (carman)/Murfitt, William (teamster); Clagris, Philip (chairmaker)/Claykes, Philip (chairmaker).
    \item "Wikify! Linking Documents to Encyclopedic Knowledge" includes a mention of the application of entity resolution to creating a semantic web.
    \item In natural language processing, entity linking, named entity disambiguation (NED), named entity recognition and disambiguation (NERD) or named entity normalization (NEN) (van: https://en.wikipedia.org/wiki/Entity_linking)
    \item Replace "person references" to "names entities" or something more formal and specific.
    \item Replace "empty value" to "null value" for clarity.
    \item Use dot notation to refer to a field of an entity $E$, e.g. $E.first_name$.
    \item Investigate "Likert scale"
    \item In 1998, Merrill Lynch cited a rule of thumb that somewhere around 80-90 of all potentially usable business information may originate in unstructured form.[1] This rule of thumb is not based on primary or any quantitative research, but nonetheless is accepted by some. (Wikipedia)
    \item Use ``acronym'' or ``glossaries'' package to create a list of acronyms which can be linked to from the text.
    \item Create an index for the thesis using the ``index'' package.
    \item It is important to note that even though we can similarity metrics to perform ``fuzzy'' matching, name variants can still cause problems and it is better to learn these first and deal with them.
\end{itemize}

\bibliographystyle{plain}
\bibliography{mybib}

\end{document}