\chapter*{Acknowledgements}
\noindent First and foremost, I would like to thank my supervisor, Arno Knobbe, for having given me the valuable opportunity to work in the Data Mining group of the Leiden Institute of Advances Computer Science, for being a mentor and keeping up with me throughout the process of writing this thesis.
I would rather not think of what would have become of me without your help ;)

Secondly, I would like to thank my parents for their love and patience.
You have always given me the liberty in which I have been able to discover my interests and pursue my ideas.

Thirdly, I would like to thank my friends and colleagues for being simply amazing.
I am very fortunate to be surrounded by such beautiful people.

Last but not least, I would like to speak out my gratitude to all the creators and innovators for the work they share.
Our views and thoughts, our identities, are shaped by the discoveries, creative thoughts and innovations of others.
It is only because of those who share that we can learn and enjoy life to the fullest.
If I were to thank every author of a piece of code or scientific article, it would easily become bigger than the main body of this thesis.
I trust that this is probably not what they would like, so I try and reach out to all of them with a simple: ``Thank you all!''.

\bigskip

\noindent To make it easier for other people to take advantage of this work, I have made the \latex source available at \url{https://github.com/benjaminvdb/master_thesis}.